### 2016-12-30 paper/evaluation.tex
WIP - updating subjects section

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. In addition, we used Maven as a
reference due to its popularity on Java projects and to automate our
evaluation. We used the Github's Search API~\cite{githubsearch} to
fetch Java projects with Maven support according to the following
criteria: (1) the primary language must be Java\footnote{In case of
projects in multiple languages, the Github API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

On Github, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects. The fourth criteria is an approximation to find
projects with Maven support. The rationale is that if the string
\emph{mvn} exists in the \emph{readme} file, it may represents a Maven
call in the instructions on how to compile (or test) the project.
Figure~\ref{fig:subject-query} illustrates the query.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={stars,language,pushed,in},
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=
    stars:>=100+language:java+mvn%20in:readme+
    pushed:>=2016-01-01+sort:stars&page=1&per_page=100

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects in Java with at least 100 stars, updated on January 1st,
    2016 (or later), and \emph{readme} file contains the string
    \emph{mvn}. Output listed in descending order of stars}
\end{figure}

As of December 12th 2016, our search criteria returned 589 subjects.
From the 589 downloaded projects, we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests.

>>>>

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. We used the Github's Search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the Github API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

On Github, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that Github users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. We
used Maven as a reference due to its popularity on Java projects and
to automate our evaluation scripts. The rationale is that if the
string \emph{mvn} exists in the \emph{readme} file, it may represent a
Maven call (\eg, to compile or test the project).
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=
    stars:>=100+language:java+mvn%20in:readme+
    pushed:>=2016-01-01+sort:stars

\end{lstlisting}
\caption{\label{fig:subject-query} Query to the Github API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

As of December 30th 2016, our search criteria returned 615 subjects.
From the 615 downloaded projects, \Fix{we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests.}
